Distributional Trees and Forests for Circular Data

### 2019-09-19 pkg/circtree/inst/wind_paper/draft/draft.Rnw
restructured application section
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@2766 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: e6b118f6c4b11cbf173bf9802a19e401325a85bb

\section{Wind Direction Forecasts}
Wind is a classical circular quantity and accurate forecasts of wind direction
are of great importance for decision-making processes and risk management,
e.g., in air traffic management or renewable energy production.

@@

\subsection{Reference Models}
Next to distributional trees for circular data and forests three other models have been applied and their 
performances have been compared based on a circular version of the continuous ranked probability 
score (CRPS).

@@

\subsection{Results}

>>>>

\section{Wind Direction Forecasts}

\subsection{Motivation}
Wind is a classical circular quantity and accurate forecasts of wind direction
are of great importance for decision-making processes and risk management,
e.g., in air traffic management or renewable energy production.

@@

\subsection{Models and Evaluation}
Next to distributional trees for circular data and forests three other models have been applied and their 
performances have been compared based on a circular version of the continuous ranked probability 
score (CRPS).

@@

Compare fitted models based on a circular version of CRPS ...

\subsection{Results}
Ibk/Vie, 1h/3h
